### 2018-01-02 derivations.tex
add pr derivatives

\newcommand{\pluseq}{\mathrel{{+}{=}}}
\newcommand{\minuseq}{\mathrel{{-}{=}}}
\newcommand{\ns}{\ensuremath{{N_{sp}}}}
\newcommand{\nr}{\ensuremath{{N_{reac}}}}
\newcommand{\conp}{CONP}
\newcommand{\conv}{CONV}
\newcommand{\dconp}{\ensuremath{\text{for \conp,}}}
\newcommand{\dconv}{\ensuremath{\text{for \conv,}}}
\newcommand{\Ru}{\ensuremath{\mathcal{R}}}

@@

@@

\Crefrange{e:dpr_mix_dt}{e:dpr_mix_de} may be recast in a more generalized form using temporary variables $\Theta_{\partial P_{r, i}, \ldots}$ and $\bar{\theta}_{\partial P_{r, i}, \ldots}$ to replace terms in the derivative:
\begin{align}
 \eqmathbox[lhs_dpr_gen][r]{\frac{\partial P_{r, i} }{\partial T } } &= \eqmathbox[rhs_dpr_gen][l]{P_{r, i} \Theta_{P_{r,i}, \partial T} + \bar{\theta}_{P_{r, i}, \partial T}} & \eqmakebox[cond_dpr_gen][r]{,} \label{e:dpr_dt} \\
 \eqmathbox[lhs_dpr_gen][r]{\frac{\partial P_{r, i} }{\partial n_j}} &= \eqmathbox[rhs_dpr_gen][l]{\frac{\bar{\theta}_{P_{r, i}, \partial n_j}}{V k_{\infty, i}} k_{0, i}} & \eqmakebox[cond_dpr_gen][r]{,} \label{e:dpr_dnj}
\end{align}
and:
\begin{subequations}
 \label{e:dpr_de}
 \begin{align}
  \eqmathbox[lhs_dpr_gen][r]{\frac{\partial P_{r, i} }{\partial V}} &= \eqmathbox[rhs_dpr_gen][l]{P_{r, i} \Theta_{P_{r,i}, \partial V} + \bar{\theta}_{P_{r, i}, \partial V}} & \eqmakebox[cond_dpr_gen][r]{\dconp} \\
  \eqmathbox[lhs_dpr_gen][r]{\frac{\partial P_{r, i} }{\partial P}} &= \eqmathbox[rhs_dpr_gen][l]{\bar{\theta}_{P_{r, i}, \partial P}} & \eqmakebox[cond_dpr_gen][r]{\dconv}
 \end{align}
\end{subequations}
with:
\begin{subequations}
\label{e:dpr_theta_mix}
\begin{align}
 \Theta_{P_{r,i}, \partial T} &= \frac{1}{T} \left(\beta_{0} - \beta_{\infty} + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) \label{e:dtheta_pr_dt} \\
 \bar{\theta}_{P_{r, i}, \partial T} &= - \frac{[C] k_{0, i} \alpha_{\ns,i}}{T k_{\infty, i}} \\
 \bar{\theta}_{P_{r, i}, \partial n_j} &= - \alpha_{\ns,i} + \alpha_{j,i} \\
 \Theta_{P_{r,i}, \partial V} &= - \frac{1}{V} \\
 \bar{\theta}_{P_{r, i}, \partial V} &= \frac{[C] k_{0, i} \alpha_{\ns,i}}{V k_{\infty, i}} \\
 \bar{\theta}_{P_{r, i}, \partial P} &= \frac{k_{0, i} \alpha_{\ns,i}}{T k_{\infty, i} \Ru}
\end{align}
\end{subequations}

For a third-body efficiency with all $\alpha_{k,i} = 1$, the reduced pressures derivatives may be expressed as~\cref{e:dpr_de}, with:
\begin{subequations}
 \label{e:dpr_theta_unity}
 \begin{align}
  \Theta_{P_{r,i}, \partial T} &= \frac{1}{T} \left(\beta_{0} - \beta_{\infty} - 1 + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) \\
  \bar{\theta}_{P_{r, i}, \partial T} &= 0 \\
  \bar{\theta}_{P_{r, i}, \partial n_j} &= 0 \\
  \Theta_{P_{r,i}, \partial V} &= 0 \\
  \bar{\theta}_{P_{r, i}, \partial V} &= 0 \\
  \bar{\theta}_{P_{r, i}, \partial P} &= \frac{k_{0, i}}{k_{\infty, i}} \frac{1}{\Ru T}
 \end{align}
\end{subequations}

If species $m$ serves as the third-body concentration, the temporary terms are:
\begin{subequations}
 \label{e:dpr_theta_spec}
 \begin{align}
  \Theta_{P_{r,i}, \partial T} &= \frac{1}{T} \left(\beta_{0} - \beta_{\infty} + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) \\
  \bar{\theta}_{P_{r, i}, \partial T} &= - \frac{[C] k_{0, i} \delta_{\ns m}}{T k_{\infty, i}} \\
  \bar{\theta}_{P_{r, i}, \partial n_j} &= - \delta_{\ns m} + \delta_{j m} \\
  \Theta_{P_{r,i}, \partial V} &= - \frac{1}{V} \\
  \bar{\theta}_{P_{r, i}, \partial V} &= \frac{[C] k_{0, i} \delta_{\ns m}}{V k_{\infty, i}} \\
  \bar{\theta}_{P_{r, i}, \partial P} &= \frac{k_{0, i} \delta_{\ns m}}{T k_{\infty, i} \Ru}
 \end{align}
\end{subequations}

@@

>>>>

\newcommand{\pluseq}{\mathrel{{+}{=}}}
\newcommand{\minuseq}{\mathrel{{-}{=}}}
\newcommand{\ns}{\ensuremath{{N_{sp}}}}
\newcommand{\nr}{\ensuremath{{N_{reac}}}}
\newcommand{\conp}{CONP}
\newcommand{\conv}{CONV}
\newcommand{\dconp}{\ifmmode\text{for \conp,}\else for \conp,\fi}
\newcommand{\dconv}{\ifmmode\text{for \conv,}\else for \conv,\fi}
\newcommand{\Ru}{\ensuremath{\mathcal{R}}}

@@

% allow page breaks for long equations:
% https://tex.stackexchange.com/questions/51682/is-it-possible-to-pagebreak-aligned-equations
\allowdisplaybreaks

@@

For a third-body concentration where all $\alpha_{k,i}=1$:
\begin{align}
 \eqmathbox[lhs_dpr_unity][r]{\frac{\partial P_{r, i} }{\partial T }} &= \eqmathbox[rhs_dpr_unity][l]{\frac{P_{r, i}}{T} \left(\beta_{0} - \beta_{\infty} - 1 + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right)} & \eqmakebox[cond_dpr_unity][r]{,} \label{e:dpr_unity_dt} \\
 \eqmathbox[lhs_dpr_unity][r]{\frac{\partial P_{r, i} }{\partial n_j }} &= \eqmathbox[rhs_dpr_unity][l]{0} & \eqmakebox[cond_dpr_unity][r]{,} \label{e:dpr_unity_dnj}
\end{align}
and:
\begin{subequations}
 \label{e:dpr_unity_de}
 \begin{align}
  \eqmathbox[lhs_dpr_unity][r]{\frac{\partial P_{r, i} }{\partial V }} &= \eqmathbox[rhs_dpr_unity][l]{0} & \eqmakebox[cond_dpr_unity][r]{\dconp}\\
  \eqmathbox[lhs_dpr_unity][r]{\frac{\partial P_{r, i} }{\partial P }} &= \eqmathbox[rhs_dpr_unity][l]{\frac{k_{0, i}}{k_{\infty, i}} \frac{1}{\Ru T}} & \eqmakebox[cond_dpr_unity][r]{\dconv}
 \end{align}
\end{subequations}

Finally, for species $m$ as the third-body:
\begin{align}
 \eqmathbox[lhs_dpr_spec][r]{\frac{\partial P_{r, i} }{\partial T }} &= \eqmathbox[rhs_dpr_spec][l]{\frac{P_{r, i}}{T} \left(\beta_{0} - \beta_{\infty} + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) - \frac{[C] k_{0, i} \delta_{\ns m}}{T k_{\infty, i}}} & \eqmakebox[cond_dpr_spec][r]{,} \label{e:dpr_spec_dt} \\
 \eqmathbox[lhs_dpr_spec][r]{\frac{\partial P_{r, i} }{\partial n_j }} &= \eqmathbox[rhs_dpr_spec][l]{\frac{k_{0, i}}{V k_{\infty, i}} \left(- \delta_{\ns m} + \delta_{j m}\right)} & \eqmakebox[cond_dpr_spec][r]{,} \label{e:dpr_spec_dnj}
\end{align}
and:
\begin{subequations}
 \label{e:dpr_spec_de}
 \begin{align}
  \eqmathbox[lhs_dpr_spec][r]{\frac{\partial P_{r, i} }{\partial V }} &= \eqmathbox[rhs_dpr_unity][l]{- \frac{P_{r, i}}{V} + \frac{[C] k_{0, i} \delta_{\ns m}}{V k_{\infty, i}}} & \eqmakebox[cond_dpr_spec][r]{\dconp}\\
  \eqmathbox[lhs_dpr_spec][r]{\frac{\partial P_{r, i} }{\partial P }} &= \eqmathbox[rhs_dpr_unity][l]{\frac{k_{0, i} \delta_{\ns m}}{T k_{\infty, i} \Ru}} & \eqmakebox[cond_dpr_spec][r]{\dconv}
 \end{align}
\end{subequations}

\Crefrange{e:dpr_mix_dt}{e:dpr_spec_de} may be recast in a more generalized form using temporary variables $\Theta_{\partial P_{r, i}, \ldots}$ and $\bar{\theta}_{\partial P_{r, i}, \ldots}$ to replace terms in the derivative:
\begin{align}
 \eqmathbox[lhs_dpr_gen][r]{\frac{\partial P_{r, i} }{\partial T } } &= \eqmathbox[rhs_dpr_gen][l]{P_{r, i} \Theta_{P_{r,i}, \partial T} + \bar{\theta}_{P_{r, i}, \partial T}} & \eqmakebox[cond_dpr_gen][r]{,} \label{e:dpr_dt} \\
 \eqmathbox[lhs_dpr_gen][r]{\frac{\partial P_{r, i} }{\partial n_j}} &= \eqmathbox[rhs_dpr_gen][l]{\frac{\bar{\theta}_{P_{r, i}, \partial n_j}}{V k_{\infty, i}} k_{0, i}} & \eqmakebox[cond_dpr_gen][r]{,} \label{e:dpr_dnj}
\end{align}
and:
\begin{subequations}
 \label{e:dpr_de}
 \begin{align}
  \eqmathbox[lhs_dpr_gen][r]{\frac{\partial P_{r, i} }{\partial V}} &= \eqmathbox[rhs_dpr_gen][l]{P_{r, i} \Theta_{P_{r,i}, \partial V} + \bar{\theta}_{P_{r, i}, \partial V}} & \eqmakebox[cond_dpr_gen][r]{\dconp} \\
  \eqmathbox[lhs_dpr_gen][r]{\frac{\partial P_{r, i} }{\partial P}} &= \eqmathbox[rhs_dpr_gen][l]{\bar{\theta}_{P_{r, i}, \partial P}} & \eqmakebox[cond_dpr_gen][r]{\dconv}
 \end{align}
\end{subequations}
with:
\begin{align}
 \label{e:dpr_theta}
 \Theta_{P_{r,i}, \partial T} &=
 \begin{dcases}
  \frac{1}{T} \left(\beta_{0} - \beta_{\infty} + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) & \text{if mix,} \\
  \frac{1}{T} \left(\beta_{0} - \beta_{\infty} - 1 + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) & \text{if all $\alpha_{k,i}$ = 1,} \\
  \frac{1}{T} \left(\beta_{0} - \beta_{\infty} + \frac{E_{a, 0}}{T \Ru} - \frac{E_{a, \infty}}{T \Ru}\right) & \text{for species $m$}
 \end{dcases} \\
 \bar{\theta}_{P_{r, i}, \partial T} &=
 \begin{dcases}
  \eqmathbox[theta_pr_bar_dt][l]{- \frac{[C] k_{0, i} \alpha_{\ns,i}}{T k_{\infty, i}}} & \text{if mix,} \\
  \eqmathbox[theta_pr_bar_dt][c]{0} & \text{if all $\alpha_{k,i}$ = 1,} \\
  \eqmathbox[theta_pr_bar_dt][l]{- \frac{[C] k_{0, i} \delta_{\ns m}}{T k_{\infty, i}}} & \text{for species $m$}
 \end{dcases} \\
 \bar{\theta}_{P_{r, i}, \partial n_j} &=
 \begin{dcases}
  \eqmathbox[theta_pr_bar_dnj][l]{- \alpha_{\ns,i} + \alpha_{j,i}} & \text{if mix,} \\
  \eqmathbox[theta_pr_bar_dnj][c]{0} & \text{if all $\alpha_{k,i}$ = 1,} \\
  \eqmathbox[theta_pr_bar_dnj][l]{- \delta_{\ns m} + \delta_{j m}} & \text{for species $m$}
 \end{dcases} \\
 \Theta_{P_{r,i}, \partial V} &=
 \begin{dcases}
  \eqmathbox[Theta_pr_bar_dv][l]{- \frac{1}{V}} & \text{if mix,} \\
  \eqmathbox[Theta_pr_bar_dv][c]{0} & \text{if all $\alpha_{k,i}$ = 1,} \\
  \eqmathbox[Theta_pr_bar_dv][l]{- \frac{1}{V}} & \text{for species $m$}
 \end{dcases} \\
 \bar{\theta}_{P_{r, i}, \partial V} &=
 \begin{dcases}
  \eqmathbox[theta_pr_bar_dv][l]{\frac{[C] k_{0, i} \alpha_{\ns,i}}{V k_{\infty, i}}} & \text{if mix,} \\
  \eqmathbox[theta_pr_bar_dv][c]{0} & \text{if all $\alpha_{k,i}$ = 1,} \\
  \eqmathbox[theta_pr_bar_dv][l]{\frac{[C] k_{0, i} \delta_{\ns m}}{V k_{\infty, i}}} & \text{for species $m$}
 \end{dcases} \\
 \bar{\theta}_{P_{r, i}, \partial P} &=
 \begin{dcases}
  \eqmathbox[theta_pr_bar_dp][l]{\frac{k_{0, i} \alpha_{\ns,i}}{T k_{\infty, i} \Ru}} & \text{if mix,} \\
  \eqmathbox[theta_pr_bar_dp][l]{\frac{k_{0, i}}{T k_{\infty, i} \Ru}} & \text{if all $\alpha_{k,i}$ = 1,} \\
  \eqmathbox[theta_pr_bar_dp][l]{\frac{k_{0, i} \delta_{\ns m}}{T k_{\infty, i} \Ru}} & \text{for species $m$}
 \end{dcases} \\
\end{align}

@@

The falloff blending factor
